Modern BTree\\ techniques

### 2020-01-18 btree/presentation.tex
DPTree

    \end{overprint}
    \end{center}
\end{frame}
\note{
    Designed for B-Tree, Masstree, Skip List, ART
}

@@

    \end{overprint}
    \end{center}
\end{frame}
\note{
    Requires also "split", "index", "remove node", "merge", "flush" deltas
}

>>>>

    \linespread{0.5}
    \vspace{0.5cm}
    \color{black}\fontsize{6pt}{0}\selectfont
        Huanchen Zhang, David G. Andersen, Andrew Pavlo, Michael Kaminsky, Lin
        Ma, and Rui Shen. 2016. Reducing the Storage Overhead of Main-Memory
        OLTP Databases with Hybrid Indexes. In Proceedings of the 2016
        International Conference on Management of Data (SIGMOD ’16).
        Association for Computing Machinery, New York, NY, USA, 1567–1581.
    \linespread{1.5}

    \end{center}
\end{frame}
\note{
    Designed for B-Tree, Masstree, Skip List, ART
}

@@

    \linespread{0.5}
    \vspace{0.5cm}
    \color{black}\fontsize{6pt}{0}\selectfont
        Levandoski, Justin Lomet, David Sengupta, Sudipta. (2012). The Bw-Tree:
        A B-tree for New Hardware Platforms. Proceedings - International
        Conference on Data Engineering. 10.1109/ICDE.2013.6544834.
    \linespread{1.5}

    \end{center}
\end{frame}
\note{
    Requires also "split", "index", "remove node", "merge", "flush" deltas
}

    \begin{center}
    \textbf{DPTree}
    \vspace{1cm}

        \onslide<2>
        \begin{tikzpicture}[]
            \node[btree-branch-node] (node1) {};

            \node[btree-leaf-node, below=0.5cm of node4.south west, xshift=-0.2cm] (node9) {};
            \node[btree-leaf-node, below=0.5cm of node4.south east, xshift=0.2cm] (node10) {};
            \coordinate[above=0.25cm of node5] (left-point);
            \coordinate[above=0.25cm of node10] (right-point);

            \draw[dashed] ([xshift=-2cm]left-point) -- ([xshift=2cm]right-point);
        \end{tikzpicture}

        \onslide<3>
        \begin{tikzpicture}[]
            \node[btree-branch-node] (node1) {};

            \node[btree-leaf-node, below=0.5cm of node4.south west, xshift=-0.2cm] (node9) {};
            \node[btree-leaf-node, below=0.5cm of node4.south east, xshift=0.2cm] (node10) {};
            \coordinate[above=0.25cm of node5] (left-point);
            \coordinate[above=0.25cm of node10] (right-point);

            \draw[dashed] ([xshift=-2cm]left-point) -- ([xshift=2cm]right-point);

            \smallbtree{1}{1.5}{left=6cm of node1}{}{}{blue-box}
            \node[draw, minimum width=0.5cm, minimum height=0.5cm, rounded corners=0.1cm, below=1.5cm of nodebox1.south] (log2) {};
            \node[draw, minimum width=0.5cm, minimum height=0.5cm, rounded corners=0.1cm, right=0.5cm of log2] (log3) {};
            \node[draw, minimum width=0.5cm, minimum height=0.5cm, rounded corners=0.1cm, left=0.5cm of log2] (log1) {};
            \draw[->, btree-line] (nodebox1.south) -- (log1);
            \draw[->, btree-line] (nodebox1.south) -- (log2);
            \draw[->, btree-line] (nodebox1.south) -- (log3);
        \end{tikzpicture}

    \end{overprint}
    \end{center}
\end{frame}
